### 2023-01-31 manuscript.tex
more FDO references [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/8ed1966988bc19593b6e558205553033af6267a7.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/8ed1966988bc19593b6e558205553033af6267a7/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4058378332

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/36d2cc87aca77995c39b6fea4ee9a6aa69587b8e/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/36d2cc87aca77995c39b6fea4ee9a6aa69587b8e}{stain/2022-fdo-paper@36d2cc8}
on January 31, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/8ed1966988bc19593b6e558205553033af6267a7/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/8ed1966988bc19593b6e558205553033af6267a7}{stain/2022-fdo-paper@8ed1966}
on January 31, 2023.
